---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{css2r}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install the development version of `{css2r}` like so:

```{r, eval=FALSE}
remotes::install_github("ThinkR-open/css2r")
```

## Extract CSS properties from a webpage

```{r}
library(css2r)

thinkr <- css2r$new(url = "https://thinkr.fr")
```

### Extract CSS files

```{r}
thinkr$domain_css_links
```

### Extract top colors

```{r}
thinkr$top_colors
```
### Show shiny theme

```{r}
cat(thinkr$shiny_code)
```

## Run the application

You can launch the application by running:

```{r, eval = FALSE}
css2r::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

## Code of Conduct
  
Please note that the css2r project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
